Proposed Solution

### 2017-01-21 CAV17/secs/arch.tex
cav17: updated small

\para{Rule refinement.}
The checker is used to detect rule violations in the configuration
files of interest. The inputs of the checker are the learned rules 
and the target configuration file to verify.
It generates a report (as shown in $\S$\ref{sec-motiv}) about 
whether it finds any error, \eg, rule violations 
or some suspicious values (\eg, singular value anomaly).
As shown in Figure~\ref{fig-overview},
there are two sub-modules in the checker. They are responsible for
checking rule violations and suspicious values, respectively.
In our experience, we found learned rules could be significantly reused
to check different configuration files, thus improving our usability.

>>>>

\para{Rule refinement.}
\ennan{It seems so far I do not know how exactly this part works. 
Maybe we can write through this part after finish the 
section 6.}
